D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-16 ootavacuous.tex
Adjust roadmap in Introduction
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This in turn leads to
Section~\ref{sec:C++ Compilers}, which describes properties of the tool
commonly used to create hardware executions with the proper relationship
to a given set of abstract executions, namely  the compiler.
Section~\ref{sec:Hardware Dependencies, Instruction Ordering, and the
Fundamental Property}
then combines hardware dependencies and instruction ordering to arrive
at the fundamental property of semantic dependencies.

@@

Finally,
Section~\ref{sec:Conclusion}
presents concluding remarks.
% @@@ Future directions at some point.

>>>>

This in turn leads to
Section~\ref{sec:C++ Compilers}, which describes properties of the tool
commonly used to create hardware executions with the proper relationship
to a given set of abstract executions, namely  the compiler.
Section~\ref{sec:Hardware Dependencies, Instruction Ordering, and the
Fundamental Property}
then combines hardware dependencies and instruction ordering to arrive
at the fundamental property of semantic dependencies, which
Section~\ref{sec:A Definition of Semantic Dependency} uses to
arrive at a definition of the term ``semantic dependency''.

@@

Finally,
Section~\ref{sec:Future Directions}
lists a few possible future directions for this work and
Section~\ref{sec:Conclusion}
presents concluding remarks.
